\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Se-eun Yoon}
\address{Email: seeuny@ucsd.edu}
\address{Web: https://seeuny.com}

\begin{document}

% Education

\begin{rSection}{Education}
{\bf Korea Advanced Institute of Science and Technology (KAIST)} \hfill \textit{Aug. 2020} 
\\M.S. in Electrical Engineering
\\\textit{Advisor: Prof. Yung Yi}
\\\textit{Co-advisor: Prof. Kijung Shin}

{\bf Korea Advanced Institute of Science and Technology (KAIST)} \hfill \textit{Aug. 2018} 
\\B.S. in Electrical Engineering (Summa Cum Laude)

\end{rSection}

\begin{rSection}{Awards \& Honors}
\textbf{Dean's List} \hfill \textit{ Spring 2015, Fall 2015, Spring 2016, Fall 2016} 
\\Top 3\% in KAIST EE

{\bf Department Honors Scholarship} \hfill {\em Spring 2015, Spring 2016} 
\\Top 3 in KAIST EE
\end{rSection}

% Research Interests

\begin{rSection}{Research Interests}
Machine learning, data mining, social network analysis, information retrieval, reinforcement learning

\end{rSection}

% Publications

\begin{rSection}{International Publications}
	\begin{enumerate}
		
	\item Structural Patterns and Generative Models of Real-world Hypergraphs \\
	Manh Tuan Do, \underline{Se-eun Yoon}, Bryan Hooi, and Kijung Shin\\
	\textbf{KDD 2020} 
		
		
	\item How Much and When Do We Need Higher-order Information in Hypergraphs? A Case Study on Hyperedge Prediction \\
	\underline{Se-eun Yoon}, Hyungseok Song, Kijung Shin, and Yung Yi\\
	\textbf{WWW 2020}
	
	\item Solving Continual Combinatorial Selection via Deep Reinforcement Learning\\
	Hyungseok Song, Hyeryung Jang, Hai H. Tran, \underline{Se-eun Yoon}, Kyunghwan Son, Donggyu Yun, Hyoju Chung, and Yung Yi\\
	\textbf{IJCAI 2019}
	\end{enumerate}
\end{rSection}


\begin{rSection}{Domestic Publications}
	\begin{enumerate}
	\item Energy Consumption at UAVs: A Deep Learning Approach\\
	\underline{Se-eun Yoon}, Daewoo Kim, and Yung Yi\\
	\textbf{KSC 2017}\footnote{Korea Software Congress}
	
	\item AI-based Drone Object Tracking System: Design and Implementation\\
	Daewoo Kim, Wanju Kang, Yoonpyo Koo, Jihwan Bang, Kyunghwan Sohn, David Hostallero, \underline{Se-eun Yoon}, Hyunho Yeo, Jaehyung Ha, Nansol Seo, Dongsu Han and Yung Yi\\
	\textbf{KICS 2017}\footnote{The Journal of Korean Institute of Communications and Information Society}
	
	\item On the Efficiency of Running Machine Learning Tasks for Drone-based Target Tracking: Cloud-based vs. Drone-based\\
	Kyunghwan Sohn, David Hostallero, Daewoo Kim, Wanju Kang, Yoonpyo Koo, Jihwan Bang, \underline{Se-eun Yoon}, Hyunho Yeo, Jaehyung Ha, Nansol Seo, Dongsu Han and Yung Yi\\
	\textbf{KICS 2017}
\end{enumerate}

\end{rSection}


% Projects

\begin{rSection}{Projects}

%\textbf{COVID-19 task force}
%\hfill \textit{Mar. 2020 - Jul. 2020}\\
%\textit{Supporter: KAIST}
%\begin{itemize}
%	\item Developed methods for inferring the daily infected cases from the daily confirmed cases.
%\end{itemize}	
%	
\textbf{Application services using power consumption data}
\hfill \textit{Aug. 2018 - Jul. 2020}\\
\textit{Supporter: Korea Electric Power Corporation}
\begin{itemize}
	\item Developed a deep learning-based software that predicts the operating hours of commercial facilities from time-series data of electric power consumption. Handled noisy data with inaccurate or missing labels. Used the Oracle Database in the system.
	\item Applied various machine learning techniques, such as data preprocessing, semi-supervised learning, uncertainty estimation, clustering, and crowdsourcing.
\end{itemize}

\textbf{Learning-based framework for improving large-scale search}
\hfill \textit{Jan. 2018 - Jul. 2018}\\
\textit{Supporter: NAVER}
\begin{itemize}
	\item Developed algorithms for selecting an item among a large candidate set. Items were search engine queries. The selected item should yield greatest user satisfaction upon update of its results page.
	\item Handled the scalability issue of deep reinforcement learning methods. Applied weight sharing to neural networks to enhance performance and efficiency. Expanded the problem into set selection.
	
\end{itemize}

\textbf{Collective drone technology combining AI and 5G}
\hfill \textit{Jul. 2017 - Dec. 2017}\\
\textit{Supporter: Korean Government}
\begin{itemize}
	\item Made drones learn to follow a moving target. Implemented reinforcement learning algorithms on a drone simulator. The target was captured by a built-in camera. There were two sub-tasks: image recognition and target tracking. I focused on the target tracking part and developed algorithms based on reinforcement learning.
	\item Developed a deep learning-based energy consumption model to make drones learn energy-efficient paths. Given the state of a drone (e.g., velocity, altitude, pitch, and roll), the task was to infer its energy consumption level.
\end{itemize}

\end{rSection}


% Other research experience
\begin{rSection}{Other selected research experience}

\textbf{Undergraduate intern}
\hfill \textit{Mar. 2017 - Jul. 2017}\\
\textit{Advisor: Prof. Hyun Wook Park}
\begin{itemize}
	\item Studied the principles of magnetic resonance imaging (MRI). Focused on recent advances in cardiac MRI research and searched for ways to make it easier for humans to use.
\end{itemize}
 	
\textbf{Undergraduate intern}
\hfill \textit{Mar. 2016 - Dec. 2016}\\
\textit{Advisor: Prof. Yong Man Ro}
\begin{itemize}
	\item Studied and implemented methods for computer-aided diagnoses of breast cancer. Applied machine learning to classify mammograms as cancer or benign and image processing methods to improve prediction quality.
\end{itemize}

\textbf{Undergraduate intern}
\hfill \textit{Jan. 2016 - Feb. 2016}\\
\textit{Advisor: Prof. Dongsu Han}
\begin{itemize}
	\item Participated in a project on AI-based automatic surveillance systems. The goal was to build a system that detected fire whenever caught on a security camera. My task was to improve the accuracy of the model classifying the existence of fire within any given image.
\end{itemize}

\end{rSection}

% Teaching

\begin{rSection}{Teaching}
{\bf Teaching assistant} 
\\ - KAIST AI601 Graph Mining and Social Network Analysis \hfill \textit{Fall 2019}
\\ - KAIST EE209 Programming Structures for Electrical Engineering \hfill \textit{Spring 2019}
\\ - KAIST EE495 Individual Study \hfill \textit{Winter 2020}
\\ - KAIST EE495 Individual Study \hfill \textit{Summer 2019}
\\ - Samsung DS-KAIST AI Expert Program \hfill {\em Summer 2019}
\\ - KICS Special Lecture: Deep Learning with Tensorflow \hfill \textit{Winter 2019}

{\bf Tutor} 
\\ - KAIST EE321 Communication Engineering \hfill \textit{Fall 2017}
\\ - KAIST PH141 General Physics \hfill \textit{Spring 2016}

{\bf Instructor}
\\ - KMLA Science Camp: Physics and Mathematics  \hfill \textit{Aug. 2016, Jan. 2017, Aug. 2017}

{\bf Other activities}
\\ - KAIST Counseling Center Mentor  \hfill \textit{Sep. 2019 - Dec. 2019}
\\ - KAIST Freshman Proctor \hfill \textit{Feb. 2017 - Dec. 2017}

\end{rSection}

\begin{rSection}{Courses}
	
\textbf{Artificial intelligence} 
\\ - EE807 Special Topics in Electrical Engineering: Deep Reinforcement Learning and AlphaGo
\hfill {\em A+}
\\ - EE474 Introduction to Multimedia
\hfill {\em A+}
\\ - EE405 Electronics Design Lab: Network of Smart Systems
\hfill {\em A+}
\\ - IE646 Data Mining
\hfill {\em A}


\textbf{Theory-oriented} 
\\ - IE801 Game Theory with Engineering Applications
\hfill {\em A}
\\ - IE539 Convex Optimization
\hfill {\em A}
\\ - EE655 Economics in Communication Networks
\hfill {\em A+}
\\ - EE623 Information Theory
\hfill {\em A}
\\ - EE528 Engineering Random Processes
\hfill {\em B+}
\\ - EE432 Digital Signal Processing
\hfill {\em A+}
\\ - EE321 Communication Engineering
\hfill {\em A}
\\ - EE210 Probability and Introductory Random Processes
\hfill {\em A+}
\\ - EE204 Electromagnetics
\hfill {\em A+}
\\ - EE202 Signals and Systems
\hfill {\em A}
\\ - MAS501 Analysis for Engineers
\hfill {\em A+}
\\ - MAS201 Differential Equations and Applications
\hfill {\em A+}
\\ - MAS109 Introduction to Linear Algebra 
\hfill {\em A+}

{\bf Systems-oriented}  
\\ - EE414 Embedded Systems
\hfill {\em A+}
\\ - EE323 Computer Networks
\hfill {\em A}
\\ - EE305 Introduction to Electronics Design Lab
\hfill {\em A+}
\\ - EE303 Digital System Design
\hfill {\em A+}
\\ - EE209 Programming Structures for Electrical Engineering
\hfill {\em A+}

\textbf{Circuits \& Devices}
\\ - EE403 Analog Electronic Circuits
\hfill {\em A}
\\ - EE362 Semiconductor Devices
\hfill {\em A}
\\ - EE304 Electronic Circuits
\hfill {\em A+}
\\ - EE211 Introduction to Physical Electronics
\hfill {\em A+}
\\ - EE201 Circuit Theory
\hfill {\em A+}

\end{rSection}


% Technical skills

\begin{rSection}{Technical skills}
Python (Pytorch, Tensorflow), Julia, MATLAB, C, C++  \\
HTML, CSS, Javascript, Ruby on Rails\\
MySQL, Oracle
\end{rSection}

% Misc. 

\begin{rSection}{Misc.}
\textbf{TOEFL}
\hfill {\em July 8th, 2020}
\\- 117/120 (Reading: 29, Listening: 30, Speaking: 30, Writing: 28)

\textbf{GRE}
\hfill {\em November 6th, 2020}
\\- 168/170 on Verbal Reasoning (98\%)
\\- 170/170 on Quantitative Reasoning (96\%)
\\- 4.5/6.0 on Analytical Writing (80\%)

\textbf{Martial arts}
\\- Taekwondo 1st Dan
\\- Kendo 1st Dan

\end{rSection}

\end{document}
